### 2021-07-09 docs/manuscript/manuscript.tex
State that quantities are dimensionless
Remove redundant step

The set of interaction values was represented as adjacency matrices $W \in
\mathbb{R}^{3\times4}$ where $i$ represents a regulated node of the GRN and $j$
represents a regulator node of the GRN (Fig \ref{fig:model}A and
\ref{fig:model}B) with $w_{\textit{ij}}~\in [-10,\ 10]$ (this interval was arbitrarily
chosen and it is inherited from the model of Munteanu~et~al.~\cite{munteanu_2014}
and Cotterell~\&~Sharpe\cite{Cotterell2010}). Values in these
matrices can be negative, zero or positive and represent represion, no
interaction, or activation respectively. The magnitude of the value is
proportional to the strength of the interaction. In this study we define
a 'genotype' as the set of interaction, diffusion and degradation values that
represent a GRN.\\

@@

 \item{\bf Mutate GRN network parameters or gene product diffusion or
degradation rates randomly and evaluate fitness again.} If fitness of the
mutated GRN is greater than that of the previous GRN, save GRN and continue
mutating.

>>>>

The set of interaction values was represented as adjacency matrices $W \in
\mathbb{R}^{3\times4}$ where $i$ represents a regulated node of the GRN and $j$
represents a regulator node of the GRN (Fig \ref{fig:model}A and
\ref{fig:model}B) with $w_{\textit{ij}}~\in [-10,\ 10]$ (this interval was arbitrarily
chosen and it is inherited from the model of Munteanu~et~al.~\cite{munteanu_2014}
and Cotterell~\&~Sharpe\cite{Cotterell2010}). Values in these
matrices can be negative, zero or positive and represent represion, no
interaction, or activation respectively. The magnitude of the value is
proportional to the strength of the interaction; however, this and all other
magnitudes in our model are dimensionless. In this study we define
a 'genotype' as the set of interaction, diffusion and degradation values that
represent a GRN.\\

@@
